Minimax lower bounds for source localization

### 2017-01-18 paper.tex
Replace `t` by `s` in text.

We assume that the point source is located on a circle of circumference $T$ (a
circular domain enables us to use symmetry arguments to simplify the proof). We
can view this domain as a line, on which signals are periodic with period $T$.
The point source is therefore located somewhere within one period. We denote
the set of possible locations by $\Theta = [0, T)$. Due to the periodic nature
of the domain, a source located at position $\theta \in \Theta$ implies the
presence of sources at $t = \theta + kT$,~$\forall \, k \in \mathbb Z$.

@@

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $t = 0$, $T/m$, $2T/m$,~\dots,
$(m{-}1)T/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). The periodicity of the space ensures that we
automatically also have sensors at $T$, $T{+}T/m$,~\dots\@ The lower bounds we
provide, therefore, are for \emph{this specific sensor configuration}. For a
discussion on why this configuration might be an appropriate choice in the
minimax setting, and on non-uniform sensor placement, see
section~\ref{sec:discussion}.

@@

All signals on the aforementioned circular domain are of the form
$f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(t;\theta) = \delta(t - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be represented by a spatial impulse response (blurring would then
correspond to low-pass filtering). Let this impulse response be given by
$g(t)$. Then, the noiseless, continuous-space signal (post-filtering and
pre-sampling) is given by the convolution, $x(t; \theta) = (g*f)(t) = g(t -
\theta)$. Here, we further make the simplifying assumption that $g(t)$ has a
sufficiently restricted support, so that aliasing effects are avoided, and
$x(t; \theta)$ is always well-defined. To be precise, $g(t) = 0$ when $\abs{t}
> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < T / 2$
(the reason for the factor of $1/2$ will become clear in a later section).

The sensors sample this continuous-space shifted impulse response, with some
additive noise. We denote the noiseless sampled version of $x(t; \theta)$ by
the $m$-length vector $\v x(\theta)$:
\begin{equation} \label{eq:sampled-signal}
	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kT}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)T}{m}; \theta\Big)\bigg]^T
\end{equation}
where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. The
additive noise is given by $\v \epsilon$ (to be described shortly), and the
noisy samples are represented by $\v y$:
\begin{equation} \label{eq:sensor-obs}
	\v y = \v x(\theta) + \v \epsilon
\end{equation}
The complete signal model described in this section is summarized in
Fig.~\ref{fig:signal-model}.

@@

We now state the main result of this paper.
\begin{theorem} \label{thm:main-lb}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
	location of a point source is lower bounded by:
	\begin{equation} \label{eq:main-lower-bound}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
	\end{equation}
\end{theorem}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(t;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{T} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
example). \textcolor{blue}{In such a case, one part of the signal $x(t;\theta_0)$ will appear at
the left edge of the domain, and the remaining part will appear as the
repetition from the period $[T, 2T)$, at the right edge of the domain.} Also
note that the two signals $x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most
once, since $w < T/2$, as stated in section~\ref{sec:signal-model}.

The upper bound in~\eqref{eq:delta-bound} translates into a lower
bound for~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}
Asymptotically, we choose smaller values of $\delta$ as the number of sensors
grows large. Hence, \textcolor{blue}{neglecting edge effects} and terms of order $\delta^3$, we
tighten the bound by choosing $\delta$ as a function of the remaining variables
in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} =
\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2
w}}$, so that for $\Phi(\delta) = \delta^2$,
equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 T}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

@@

So far, we've relied on the presence of a circular domain for to make the
arguments in the proof. However, the most important requirement was that
\emph{all} parts of the impulse response should get \emph{sensed} uniformly.
So, if $\theta$ were restricted to the region $[0, T)$ (now on a linear,
non-periodic domain), and if sensors were available to sense the signal from
$[-w/2, T{+}w/2)$ (for an impulse response with restricted support as described
in section~\ref{sec:signal-model}), then the proof for sensor noise would still
fall through, albeit with slightly different constants.

@@

We can trivially expand the domain of impulse responses to which the lower
bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
continuous functions. These are functions which satisfy
\begin{equation}
	\abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
\end{equation}
for some constant $\kappa$, and for $\alpha > 0$. Using this property,
equation~\eqref{eq:delta-bound} reads
\begin{equation} \label{eq:holder-delta-bound}
	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{T} + 1\bigg).
\end{equation}
Hence, we choose $\delta = (\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
w})^{1/2\alpha}$, to procure an asymptotic lower bound
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
w}\bigg)^{1/\alpha}.
\end{equation}

@@

Another simple extension takes our problem from a one-dimensional setting to a
$d$-dimensional setting. Here, we would have $\v\theta \in [0, T)^d$, and the
$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov2009Introduction} in
the manner described in~\cite{Duchi2015Information}, we can split the minimax
risk along each of the $d$ dimensions, and bound each separately using Le Cam's
method.

@@

The lower bounding \emph{technique} gives certain inisights on the issue of
sensor placement. Suppose we wanted to achieve a higher resolution in a
restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
to place sensors \emph{not} precisely over the region, but rather in the region
corresponding to the \emph{largest change} in the impulse response. Indeed, it
is possible to derive an  approximate lower bound using Taylor's approximation,
which shows that the KL-divergence between distributions is maximized (and
hence error minimized) at regions where the slope of $x(t;\theta)$ is largest.

>>>>

We assume that the point source is located on a circle of circumference $S$ (a
circular domain enables us to use symmetry arguments to simplify the proof). We
can view this domain as a line, on which signals are periodic with period $S$.
The point source is therefore located somewhere within one period. We denote
the set of possible locations by $\Theta = [0, S)$. Due to the periodic nature
of the domain, a source located at position $\theta \in \Theta$ implies the
presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$.

@@

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $s = 0$, $S/m$, $2S/m$,~\dots,
$(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). The periodicity of the space ensures that we
automatically also have sensors at $S$, $S{+}S/m$,~\dots\@ The lower bounds we
provide, therefore, are for \emph{this specific sensor configuration}. For a
discussion on why this configuration might be an appropriate choice in the
minimax setting, and on non-uniform sensor placement, see
section~\ref{sec:discussion}.

@@

All signals on the aforementioned circular domain are of the form
$f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be represented by a spatial impulse response (blurring would then
correspond to low-pass filtering). Let this impulse response be given by
$g(s)$. Then, the noiseless, continuous-space signal (post-filtering and
pre-sampling) is given by the convolution, $x(s; \theta) = (g*f)(s) = g(s -
\theta)$. Here, we further make the simplifying assumption that $g(s)$ has a
sufficiently restricted support, so that aliasing effects are avoided, and
$x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$ when $\abs{s}
> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < S / 2$
(the reason for the factor of $1/2$ will become clear in a later section).

The sensors sample this continuous-space shifted impulse response, with some
additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
the $m$-length vector $\v x(\theta)$:
\begin{equation} \label{eq:sampled-signal}
	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kS}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)S}{m}; \theta\Big)\bigg]^T
\end{equation}
where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. The
additive noise is given by $\v \epsilon$ (to be described shortly), and the
noisy samples are represented by $\v y$:
\begin{equation} \label{eq:sensor-obs}
	\v y = \v x(\theta) + \v \epsilon
\end{equation}
The complete signal model described in this section is summarized in
Fig.~\ref{fig:signal-model}.

@@

We now state the main result of this paper.
\begin{theorem} \label{thm:main-lb}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
	location of a point source is lower bounded by:
	\begin{equation} \label{eq:main-lower-bound}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}
	\end{equation}
\end{theorem}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{S}}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kS}{m}; \theta_0\Big) - x\Big(\frac{kS}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(s;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(s;\theta_0)$ and $x(s;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{S} + 1}$, since at most a fraction $(w + 2\delta) / S$ of the $m$
sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{S} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{S} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $s=0$, for
example). \textcolor{blue}{In such a case, one part of the signal $x(s;\theta_0)$ will appear at
the left edge of the domain, and the remaining part will appear as the
repetition from the period $[S, 2S)$, at the right edge of the domain.} Also
note that the two signals $x(s;\theta_0)$ and $x(s;\theta_1)$ overlap at most
once, since $w < S/2$, as stated in section~\ref{sec:signal-model}.

The upper bound in~\eqref{eq:delta-bound} translates into a lower
bound for~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{S} + 1\bigg)} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{S} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}
Asymptotically, we choose smaller values of $\delta$ as the number of sensors
grows large. Hence, \textcolor{blue}{neglecting edge effects} and terms of order $\delta^3$, we
tighten the bound by choosing $\delta$ as a function of the remaining variables
in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 S}} =
\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2
S}{8nm\kappa^2 w}}$, so that for $\Phi(\delta) = \delta^2$,
equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 S}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

@@

So far, we've relied on the presence of a circular domain for to make the
arguments in the proof. However, the most important requirement was that
\emph{all} parts of the impulse response should get \emph{sensed} uniformly.
So, if $\theta$ were restricted to the region $[0, S)$ (now on a linear,
non-periodic domain), and if sensors were available to sense the signal from
$[-w/2, S{+}w/2)$ (for an impulse response with restricted support as described
in section~\ref{sec:signal-model}), then the proof for sensor noise would still
fall through, albeit with slightly different constants.

@@

We can trivially expand the domain of impulse responses to which the lower
bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
continuous functions. These are functions which satisfy
\begin{equation}
	\abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
\end{equation}
for some constant $\kappa$, and for $\alpha > 0$. Using this property,
equation~\eqref{eq:delta-bound} reads
\begin{equation} \label{eq:holder-delta-bound}
	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{S} + 1\bigg).
\end{equation}
Hence, we choose $\delta = (\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
w})^{1/2\alpha}$, to procure an asymptotic lower bound
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
w}\bigg)^{1/\alpha}.
\end{equation}

@@

Another simple extension takes our problem from a one-dimensional setting to a
$d$-dimensional setting. Here, we would have $\v\theta \in [0, S)^d$, and the
$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov2009Introduction} in
the manner described in~\cite{Duchi2015Information}, we can split the minimax
risk along each of the $d$ dimensions, and bound each separately using Le Cam's
method.

@@

The lower bounding \emph{technique} gives certain inisights on the issue of
sensor placement. Suppose we wanted to achieve a higher resolution in a
restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
to place sensors \emph{not} precisely over the region, but rather in the region
corresponding to the \emph{largest change} in the impulse response. Indeed, it
is possible to derive an  approximate lower bound using Taylor's approximation,
which shows that the KL-divergence between distributions is maximized (and
hence error minimized) at regions where the slope of $x(s;\theta)$ is largest.
